Denotational Semantics of General Payment Primitives, and Its Payment System

### 2022-10-19 packages/spec-haskell/yellowpaper/Paper1.tex
typo fixes

This paper is the first one of the series yellow papers about modern payment system dubbed
``semantic money''.

@@

In part\ref{part:foundation}, we shall first explore the foundation. Here we present a formal
definition of payment system and its components. We then select a few relevant approaches used in
computer science useful for modeling and defining formal specification for the payment system.

@@

This paper defines the what constitutes a modern payment system, with its payment primitives
formally specified using denotational semantics and restated using Haskell programming
language. Along with a reference implementation of the specification, we want to make a case that
marrying with the progress of computer science, the notation of money can perform its function of
medium of exchange can have a modern upgrade.

Absent of any claim on whether if such modern upgrade is needed, we ask the readers ask
ourselves a question together: with electronic money increasingly being used, should we keep
emulating the function money of its traditional quality, or could we rethink what it may be in the
information age?

>>>>

This paper is also the first one in the series of yellowpapers about modern payment system dubbed
``semantic money''.

@@

In part \ref{part:foundation}, we shall first explore the foundation. Here we present a formal
definition of payment system and its components. We then select a few relevant approaches used in
computer science useful for modeling and defining formal specification for the payment system.

@@

This paper defines the what constitutes a modern payment system, with its payment primitives
formally specified using denotational semantics and restated using Haskell programming
language. Along with a reference implementation of the specification, we want to make a case that
marrying with the progress of computer science, the way of money performing its function of medium
of exchange can have a modern upgrade.

Absent of any claim on whether if such modern upgrade is needed, we invite the readers to ask
ourselves a question together: with electronic money increasingly being used, should we keep
emulating the function money of its traditional quality, or could we rethink what it may be in the
information age?
